---
title: "The Association Between Tuberculosis and Type II Diabetes and Risk Factors in Shanghai, China"
author: "Rui Huang (rh2916), Hanbo Qiu (hq2163), Annie Yu (xy2404), Dana Zeng (dz2399), Coco Zou (xz2809)"
date: "November 8, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(incidence)
library(patchwork)
library(survival)
library(survminer)

```

**Import data:**

```{r}
load("dm.RData")
```

```{r}
df_combine = dm_base %>% 
  rename(
    subject_id = JiBenCID,
    glu_average = fastglu, 
    weight_initial = tizhong_1st, 
    weight_average = tizhong, 
    height = ShenGao, 
    glu_initial = kfxt_1st,
    gender = xingbie,
    district = GuanLiQX,
    sys_pressure = Sbp,
    dia_pressure = Dbp,
    exercise_time = xiuxiansj,
    exercise = xiuxiantl,
    drug_insulin = insulin,
    drug_oral_sulfo = sulfonylurea,
    drug_oral_biguanide = biguanide,
    drug_oral_glu = glu_inhib,
    retina = reti, 
    skin = derm, 
    vessel = vesl, 
    nerve = neur,
    kidney = neph, 
    depression = depress,
    dmtime = quezhensj,
    birthyear  = birth_year,
    birthmon = birth_mon,
    dmdatayear = rucu_year,
    dmdatamon = rucu_mon,
    dmdataage = rucuage,
    drug_order = fuyaoqk) %>% 
  mutate(
    bmi_initial = weight_initial/(height/100)^2, 
    bmi_average = weight_average/(height/100)^2, 
    bmi_change = bmi_average - bmi_initial,
    glu_change = glu_average - glu_initial,
    tb = ifelse(censer == 1, "No", "Yes"),
    exercise = as.factor(exercise),
    drug_oral_name  = case_when(drug_oral_sulfo == "1" & drug_oral_biguanide == "0" & drug_oral_glu == "0" ~"sulfonylurea",
                           drug_oral_biguanide == "1" & drug_oral_sulfo == "0" & drug_oral_glu == "0" ~ "biguanide",
                           drug_oral_glu == "1" & drug_oral_biguanide == "0" & drug_oral_sulfo == "0" ~ "glu_inhib",
                           drug_oral_sulfo == "1" & drug_oral_biguanide == "1" & drug_oral_glu == "0" ~"sulfonylurea&biguanide",
                           drug_oral_biguanide == "1" & drug_oral_sulfo == "0" & drug_oral_glu == "1" ~ "biguanide&glu_inhib",
                           drug_oral_sulfo == "1" & drug_oral_biguanide == "0" & drug_oral_glu == "1" ~"sulfonylurea&glu_inhib",
                           drug_oral_sulfo == "1" & drug_oral_biguanide == "1" & drug_oral_glu == "1" ~"sulfonylurea&glu_inhib&biguanide",
                           TRUE ~ "NA"),
    drug = drug_oral_biguanide + drug_oral_biguanide + drug_oral_glu + drug_insulin,
    retina = as.numeric(retina),
    skin = as.numeric(skin),
    vessel = as.numeric(vessel),
    nerve = as.numeric(nerve),
    kidney = as.numeric(kidney),
    complications = retina + skin + vessel + nerve + kidney + depression,
    complications = as.factor(complications),
    drug_order = as.factor(drug_order)
  )


levels(df_combine$exercise) <- list('1' = 1,  '2' = 2, '3' = c(3,4))

save(df_combine,file='./data/df_combine.RData')
```

### Exercise and K-M plot

Compare male and female mean for exercise by t.test

```{r}
male_exercise = df_combine %>% 
  filter(gender == 1) %>% 
  mutate(exercise = as.numeric(exercise))
    
female_exercise = df_combine %>% 
  filter(gender == 2) %>% 
  mutate(exercise = as.numeric(exercise))

var.test(male_exercise$exercise,female_exercise$exercise, alternative = "two.sided")

t.test(male_exercise$exercise,female_exercise$exercise, var.equal=FALSE, paired=FALSE) 
```

Compare male and female mean for exercise_time by t.test

```{r}
var.test(male_exercise$exercise_time,female_exercise$exercise_time, alternative = "two.sided")

t.test(male_exercise$exercise_time,female_exercise$exercise_time, var.equal=FALSE, paired=FALSE) 
```

Compare male and female mean for exercise_time*exercise by t.test

```{r}
male_exercise = male_exercise %>% mutate(total_exercise = exercise * exercise_time)
female_exercise = female_exercise %>% mutate(total_exerise = exercise * exercise_time)
var.test(male_exercise$total_exercise,female_exercise$total_exerise, alternative = "two.sided")
t.test(male_exercise$total_exercise,female_exercise$total_exercise, var.equal=FALSE, paired=FALSE) 
```


Make exercise distribution plot

```{r}
df_combine %>% 
  mutate(exercise = as.numeric(exercise),
         total_exercise = exercise * exercise_time,
         gender = as.factor(gender)) %>% 
  ggplot(aes(x = total_exercise, color = gender)) +
  geom_density()

df_combine %>% 
  mutate(exercise = as.numeric(exercise),
         total_exercise = exercise * exercise_time,
         gender = as.factor(gender)) %>% 
  ggplot(aes(x = gender, y = total_exercise, color = gender)) +
  geom_boxplot()

df_combine %>% 
  mutate(exercise = as.numeric(exercise),
         gender = as.factor(gender)) %>% 
  ggplot(aes( x = gender, y = exercise)) +
  geom_violin()

df_combine %>% 
  mutate(gender = as.factor(gender)) %>% 
  ggplot(aes( x = gender, y = exercise_time)) +
  geom_violin()
```

Make tb vs exercise plot

```{r}
df_combine %>% 
  mutate(exercise = as.numeric(exercise),
         total_exercise = exercise * exercise_time,
         gender = as.factor(gender)) %>% 
  ggplot(aes(x = tb, y = total_exercise, color = gender)) +
  geom_boxplot() +
  facet_grid(.~gender)

```

K-M plot

```{r}
df_combine$survival = with(df_combine, Surv(days, tb == "Yes"))

km <- survfit(survival ~ 1, data = df_combine, conf.type = "log-log")
km_by_gender <- survfit(survival ~ gender, data = df_combine, conf.type = "log-log")


ggsurvplot(km_by_gender, data = df_combine, risk.table = F, pval = T, ylab = "Probability of getting TB", ylim = c(0.9, 1.0), legend.labs = c("Male", "Female"))
```


## Incidence of tb...
```{r}

```


##Compare diabete and age...

Make a diabete-age distribution plot
```{r}
plot_dia_d<-df_combine %>% 
  mutate(dmage = as.numeric(dmage),
         gender = as.factor(gender)) %>% 
  ggplot(aes(x = dmage, fill= gender)) +
  geom_density()+
  facet_grid(.~gender)

plot_dia_v<-df_combine %>% 
  mutate(dmage = as.numeric(dmage),
         gender = as.factor(gender)) %>% 
  ggplot(aes(x = gender, y= dmage, fill=gender)) +
  geom_boxplot()

plot_dia_d+plot_dia_v


```

Make a tb-age distribution plot(QQQQQ)
```{r}
df_tbage <-df_combine %>% 
  na.omit(`_COL19`) %>% 
  rename(tbtime = `_COL19`) %>% 
  mutate(#separate(tbtime, into = c("tb_year", "tb_month", "tb_day"), sep = "-"),
         gender = as.factor(gender),
         birthyear = as.numeric(birthyear)) 
  
ggplot(df_tbage, aes(x= birthyear, y =tbtime, fill = gender)) +
 geom_violin()+
  facet_grid(.~gender)

  
  
```


Make a tb-diabete age distribution plot
```{r}
df_combine %>% 
  mutate(dmage = as.numeric(dmage),
         tb = as.factor(tb),
         gender = as.factor(gender)) %>% 
  ggplot(aes( x=dmage,y=tb,group=gender) )+ 
  scale_fill_brewer(palette = "Spectral") + 
  geom_col(aes(fill=gender))

df_combine %>% 
  mutate(dmage = as.numeric(dmage),
         gender = as.factor(gender)) %>% 
ggplot(aes(x = tb, y = dmage, color = gender)) +
  geom_boxplot()+
  facet_grid(.~gender)
```

