---
title: "Cox Analysis and Visualization"
author: "DZ"
date: "November 25, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("survival")
library("survminer")
library(tidyverse)
```

### Multivariate Cox Regrassion and Interpretation
```{r}
load('./data/df_combine.RData')

df <- df_combine %>% 
  mutate(age = 2018-as.numeric(birthyear)) %>% 
  mutate(complications = as.numeric(complications)) %>% 
  mutate(exercise = as.numeric(exercise))

cox <- coxph(Surv(days, censer) ~ complications+gender+exercise+age+drug, data =df)

```

#### The global test statistic is given by:
```{r}
broom::glance(cox) %>%
  select(statistic.log,p.value.log,statistic.sc,p.value.sc,statistic.wald,p.value.wald,r.squared) %>% 
  knitr::kable(digits = 3)
```

#### The summary of Cox Regression 
```{r}

broom::tidy(cox) %>% 
  mutate(exp_estimate = exp(estimate)) %>% 
  select(term,exp_estimate, std.error, statistic, p.value) %>% 
knitr::kable(digits = 3)

```



The p-value for all three overall tests (likelihood, Wald, and score) are significant, indicating that the model is significant. These tests evaluate the omnibus null hypothesis that all of the $\beta$ are 0, and therefore the omnibus null hypothesis is soundly rejected.

In the multivariate Cox analysis, the all covariates remain significant (p < 0.05).

The p-value for exercise is less than 2e-16, with a hazard ratio HR = exp(coef) = 0.818, indicating a relationship between the exercise status and decreased risk of death.  When holding the other covariates constant, exercising more than 2 hour a week (exercise=3) reduces the hazard by nearly 20%. We conclude that, exercising more than 2 hour a week is associated with good prognostic.

The p-value for gender is less than 2e-16, with a hazard ratio HR = exp(coef) = 0.919, indicating a relationship between the patients’ sex and decreased risk of death.  When holding the other covariates constant, being female (sex=2) reduces the hazard by nearly 8%. We conclude that, being female is associated with good prognostic.

The p-value for drug is less than 2e-16, with a hazard ratio HR = exp(coef) = 0.909, indicating a relationship between the number of andiabetic drugs that the patient takes and decreased risk of death. When holding the other covariates constant, taking four antidiabetic medications (drug=4) reduces the hazard by nearly 10%. We conclude that, taking antidiabetic medication is associated with good prognostic.

### Visualizing the estimated distribution of survival times
```{r}
new_data <- cbind(
  complications = mean(df$complications),
  gender = mean(df$gender), 
  exercise = mean(df$exercise) ,
  age =mean(df$age) ,
  drug = mean(df$drug)
)
ggsurvplot(survfit(cox), data =new_data, palette  = "#2E9FDF",conf.int = T,
           ggtheme = theme_minimal() )+
  ggtitle('Overall Survival curve')
```

