---
title: "Descriptive_Statistics"
author: "Rui Huang"
date: "December 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
load('./data/df_combine.Rdata')
df = df_combine %>% 
  filter(district != "") %>% 
  mutate(tb = fct_recode(tb, '1'= 'Yes', '0'='No')) %>% 
  mutate(tb=as.character(tb),
         tb=as.numeric(tb)) 

# person_years
summary(df$days)
mean_follow_up_year = mean(df$days)/365
sum_follow_up_year = sum(df$days)/365

# tb summary
summary(df$tb)
sum_tb = sum(df$tb)

# all participants
nrow(df)

# overall incidence
overall_incidence = sum_tb/sum_follow_up_year

# male incidence
df_male = df %>% filter(gender == 'Male')
male_incidence = sum(df_male$tb)/(sum(df_male$days)/365)

# female incidence
df_female = df %>% filter(gender == 'Female')
female_incidence = sum(df_female$tb)/(sum(df_female$days)/365)

```

With an average following-up period of `r mean(df$days)/365` year (range: `r min(df$days)/365` to `r max(df$days)/365` years, `r sum(df$tb)` TB cases were recorded among `r nrow(df)` T2DM patients from `r sum(df$days)/365` person-years follow-up. The overall incident rate of TB was `r 100000*(sum(df$tb)/(sum(df$days)/365))` per 100 000 person-years with `r 100000*(sum(df_male$tb)/(sum(df_male$days)/365))` per 100 000 person-years for men, and `r 100000*(sum(df_female$tb)/(sum(df_female$days)/365))` per 100 000 person-years for women.

