---
title: "Exercise"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(survminer)
library(survival)
library(plotly)
library(GGally)
library(tmap)
library(rgdal)
library(maptools)
library(rgeos)
library(survivalAnalysis)
```


```{r, message=F, warning=F, echo=F}
# Download data
load('./data/df_combine.Rdata')
```


```{r, message=F, warning=F, echo=F}
df_exercise = df_combine %>% 
  mutate(exercise = as.numeric(exercise),
         total_exercise = exercise * exercise_time,
         gender = as.factor(gender))
```


```{r, message=F, warning=F, echo=F}
# Incidence
df_incidence  <- df_exercise %>% 
  mutate(tb = fct_recode(tb, '1'= 'Yes', '0'='No')) %>% 
  mutate(tb=as.character(tb),
         tb=as.numeric(tb)) %>% 
  group_by(total_exercise) %>% 
  summarise(tb_sum = sum(tb),
           incidence = tb_sum/n()) %>% 
  ungroup()
```

### K-M plot for different exercise people

```{r, message=F, warning=F, echo=F}
df_exercise = df_exercise %>% 
  inner_join(df_incidence, by = "total_exercise")

df_exercise$survival = with(df_exercise, Surv(days, tb == "Yes"))

km <- survfit(survival ~ 1, data = df_exercise, conf.type = "log-log")
km_by_exercise <- survfit(survival ~ exercise, data = df_exercise, conf.type = "log-log")

km_by_exercise_time <- survfit(survival ~ exercise_time, data = df_exercise, conf.type = "log-log")

plot_exercise_level <- GGally::ggsurv(km_by_exercise, main = "Kaplan-Meier Curve for getting TB of different exercise level")
plotly::ggplotly(plot_exercise_level)

plot_exercise_time <- GGally::ggsurv(km_by_exercise_time, main = "Kaplan-Meier Curve for getting TB of different exercise time")
plotly::ggplotly(plot_exercise_time)
```

The plot shows that people with lower exercise level have higher probability of getting TB, which show that exercise is important to preventing TB. However, people with over 2 hours exercise time have higher probability of getting TB. That may be because that people spending more time on exercise have more probability touching other people and getting infection.


### Show exercise difference among gender and age


```{r, message=F, warning=F, echo=F}
plot_exer = ggplot(df_exercise, aes(x = dmage, y =total_exercise, colour=dmage)) +
    geom_histogram(stat = "identity", width = .6) +
    labs(title="The average exercise vs age",
         x = "age") +facet_wrap(~gender)
ggplotly(plot_exer)


box_exercise = df_exercise %>% 
  mutate(mean_exercise = mean(total_exercise)) %>% 
  ggplot(aes(x = gender, y = bmi_average, fill = tb)) +
  geom_boxplot() +
  scale_y_continuous(limits=c(10, 40)) +
  theme_classic() +
  labs(title="The average exercise vs gender and tb",
         x = "Gender",
         y = "Average Exercise") 

ggplotly(box_exercise)
```


Average exercise of female is slightly higher than male.

### map


```{r, message=F, warning=F, echo=F}
x = df_exercise %>% 
  group_by(district) %>% 
  summarise(exercise_sum = sum(total_exercise)) %>% 
  ungroup()

levels(x$district) <- list("Huangpu" = 310101, "Xuhui" = 310104, "Changning" = c(310105, 310106), "Putuo" = 310107, "Zhabei" = 310108, "Hongkou" = 310109, "Yangpu" = 310110, "Minhang" = 310112, "Baoshan" = 310113,  "Pudong" = c(310115, 310119), "Jiading" = 310114, "Jinshan" = 310116, "Songjiang" = 310117, "Qingpu" = 310118, "Fengxian" = 310120, "Chongming" = 310230)
```

```{r, message=F, warning=F, echo=F}
sh <- readOGR('./data/shanghai_shapefile/shang_dis_merged.shp',verbose = F)
##Translating and Adding two missing two districts
sh@data <- sh@data %>% 
  mutate(Name = as.factor(Name)) %>%
  mutate(Name = fct_recode(Name, Jiading = '嘉定区',
                           Fengxian = '奉贤区',
                           Baoshan = '宝山区',
                           Chongming = '崇明县',
                           Xuhui = '徐汇区',
                           Putuo ='普陀区',
                           Yangpu = '杨浦区',
                           Songjiang = '松江区',
                           Pudong='浦东新区',
                           Hongkou = '虹口区',
                           Jinshan = '金山区',
                           Changning = '长宁区',
                           Minhang = '闵行区',
                           Zhabei = '闸北区',
                           Qingpu = '青浦区', 
                           Huangpu = '黄浦区'))


```

```{r, message=F, warning=F, echo=F}
sh$exercise_sum <- x$exercise_sum

qtm(sh, fill = "exercise_sum")
```

People from Minxing district has the highest exercise.











