---
title: "Exploratory Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(survminer)
library(survival)
library(GGally)
library(tmap)
library(rgdal)
library(maptools)
library(rgeos)
library(survivalAnalysis)
load("./data/df_combine.RData")

```

<div style="margin-bottom:50px;">
</div>

# Different Risk Factors {.tabset .tabset-fade .tabset-pills}

<div style="margin-bottom:30px;">
</div>

## Analysis of Medication Intake

<div style="margin-bottom:20px;">
</div>

```{r,message=FALSE,warning=F,echo=F}
df_drug = df_combine %>% 
  select(contains("drug"),censer,urban_rural,dmage,gender) 



p2 <- df_drug %>% 
  ggplot(aes(x = drug))+geom_histogram(color="black", fill="blue")+
  facet_grid(~factor(gender)) + 
  viridis::scale_fill_viridis(discrete = TRUE)+
  theme_classic()+
  labs(
    x = "Drug Level",
    y = "Number of People"
  )
ggplotly(p2)
```

The plot is showing that among all the people with Type II diabetes, Females are more likely to following medical orders to take medicines. The x axis shows the kinds of medicine that drug using, while y axis is the number of people. 

## Analysis of Complications
```{r,warning=F, message=F,echo=F}
df_complication <- df_combine %>% 
  mutate(retina = as.numeric(retina),
         skin = as.numeric(skin),
         vessel = as.numeric(vessel),
         nerve = as.numeric(nerve),
         kidney = as.numeric(kidney)) %>% 
  mutate(complications = retina + skin + vessel + nerve + kidney + depression) %>%
  mutate(complications = as.character(complications),
         complications = fct_collapse(complications, none='0',one='1',more_than_two= as.character(c(2:6))))
  

ggplot(df_complication, aes(x = complications, y = dmage, hue = gender)) + 
  geom_violin(aes(fill = gender), color = "blue", alpha = .5) + 
  stat_summary(fun.y = median, geom = "point", color = "blue", size = 4) +
  theme_classic()+
  labs(
    x = "Number of Complication",
    y = "Age"
  )
```

In this plot we can show that the distribution of none, one, and 'more than two' complication groups do not differ that much across age and gender. This indicates that we have much more none and one complication observations compare to 'more than two' complications group, since 'more than two' is the observation sum of three to six complications. 

## Analysis of Exercise

```{r,echo=F,warning=F}
df_exercise = df_combine %>% 
  mutate(exercise = as.numeric(exercise),
         total_exercise = exercise * exercise_time,
         gender = as.factor(gender),
         urban_rural = ifelse(urban_rural== 1, "Urban", "Rural"))

plot_exer = df_exercise %>% 
  group_by(gender, urban_rural, dmage) %>% 
  summarize(total_exercise = mean(total_exercise)) %>% 
  ungroup() %>% 
  ggplot(aes(x = dmage, y =total_exercise, color=urban_rural)) +
    geom_line() +
    labs(title="The average exercise vs age",
         x = "Age",
         y = "Exercise")+
  theme_classic() 

ggplotly(plot_exer) 
```

This plots shows the distribution of exercise amount along with different ages. Between age 25 to 80, which represents the most of samples, people from rural district has more exercise amout than urban people. The noise within below 25 range and above 80 range is probabily because the number of samples from these two ranges are too small to show a trend. 

## Initial BMI

```{r,echo=F,warning=F}
df_combine %>% 
  ggplot(aes(x = gender, y = glu_initial, fill = tb)) +
  geom_boxplot() +
  scale_y_continuous(limits=c(0, 15)) +
  theme_classic()+
  labs(
    y = "Initial Glucose Level"
  )
```

This plots shows the range of initial glucose level of different genders. The red box represents the individuals without tuberculosis while the green box represents the ones who have the disease. The median and the third quartiles of the initial glucose level are higher in TB individuals than those of samples without TB.

## Glucose Management

```{r,message=F,echo=F,warning=F}
df_combine %>% 
  mutate(urban_rural = as.factor(urban_rural)) %>% 
  filter(!is.na(district), !district %in% c("Xuhui", "Qingpu", "Jiading")) %>% 
  group_by(district) %>% 
  nest() %>% 
  mutate(models = map(data, ~glm(tb ~ gender + dmage + glu_self_monitor, data = .x, family = binomial())),
         ci = map(.x=models, ~confint(.x)),
         or = map(models, broom::tidy),
         ci = map(ci, broom::tidy)) %>% 
  select(-data,-models) %>% 
  unnest() %>% 
  filter(term == "glu_self_monitorNo") %>% 
  select(district, or = estimate, ci_low = "X2.5..", ci_high = "X97.5..") %>% 
  mutate(or = exp(or), ci_low = exp(ci_low), ci_high = exp(ci_high), district = fct_reorder(district, or)) %>% 
  ggplot(aes(x = district, y = or)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high)) +
  labs(
    title = "The estimated ORs and CIs for district in Shanghai",
    x = "District",
    y = "The estimated ORs and CIs"
  ) +
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(limits=c(0, 4))
```

For each district in Shanghai, obtain the estimate and confidence interval of the adjusted odds ratio for having tb comparing diabetes who regularly monitor glucose to those who don't monitor glucose regularly keeping all other variables fixed. The results show Huangpu district has the highest OR and Baoshan district has the lowest OR.

